I always considered the coupling between computer science and civil engineering fascinating. Back in November, I had a solid background in structural engineering and Python as tools in my hands, and zero experience on \acrfull{DRL} and Bayesian inference. I was willing to dive into unknown fields, gain new practical and theoretical knowledge, and expand my skill set. My mentors seemed more than certain that I could pull this off, and I am grateful for their trust and glad for proving them right seven months later. Of course, this amazing experience, and unique opportunity to learn and grow, would not have been the same without the contribution of many people whom I would like to thank.\\


First of all, I would like to express my gratitude to my mentors Charalampos Andriotis and Alice Cicirello for their tremendous assistance and support during this project. Their passion for the field is an ever-motivating factor that was and keeps inspiring me. They provided me with incredible insight and feedback, and their total guidance was a key factor in completing this project. I want to also thank Alfredo Nunez Vicencio for his valuable input and his constructive comments that improved significantly aspects of the project. Lastly, I am grateful for the genuine help of Ziead Metwally, who was always willing to discuss with me various challenging issues and provide me with valuable insight.\\

Last but not least, I would like to thank my friends and family, both back in Greece and the Netherlands. In particular, I am thankful to Arte for being a friend and supporter of mine for longer than I can remember, Lisa and Matteo, for the unique trips, dinners, and brunches, Giorgos and Maria, for the countless movie and board game nights we had, my good friend Kostas, for continuing to be the best candidate to discuss any new project I set my hands on, and many others I would like to include, for being part of my life and supporting me in their unique way. Special thanks to my dear friend and partly roommate Leo for being part of so many beautiful experiences, but this time also for the extra computational power he generously granted me during this project. I could not quantify the contribution of my partner Anastasia to every little or big achievement of my adult life. This one could not differ, with her support in every daily aspect and her encouragement for me to keep pushing forward, played a vital part in me completing this journey. Finally, I would like to thank my brother Nikos and my mother Zoi, who always supported and believed in me, and trying to make them proud has always been a driving factor.

\vspace{0.5cm}

\begin{flushright}
    \emph{Christos Lathourakis}\\
    \emph{Delft, July 2022}
\end{flushright}